---
title: "ProjectSTAT632"
author: "Abhishek Sendil"
date: "4/24/2022"
output:
  pdf_document: default
  word_document: default
---

```{r}
library(tidyverse)
library(ggplot2)

```


```{r}
titanic<-read_csv("titanic.csv")
```

```{r}
titanic3<-titanic %>%
  select(Survived,Pclass,Sex,Age)%>%
  mutate(Survived=factor(Survived,levels=c(0,1),labels=c("no","yes")))%>%
  mutate(Pclass=factor(Pclass))%>%
  drop_na()


```



```{r}
ggplot(titanic3,aes(x=Age,y=Survived,color=Sex))+
geom_point(alpha=0.15)+
geom_smooth(method="glm",method.args=list(family="binomial"),se=FALSE)+
theme_bw()

```







# Summary Statitics : BoxPlot,ScatterPlot Bar Plot

```{r}
plot(Survived~Age,data=titanic3)

```
```{r}

ggplot(titanic3,aes(x=Pclass,fill=Survived))+
  geom_bar(posistion="fill") +
xlab("Ticket Class") + ylab("Proportion")

```


```{r}
ggplot(titanic3 ,aes(x=Sex,fill=Survived))+
 geom_bar(position="fill")
```




```{r}
glm2<-glm(Survived~Age+Sex+Pclass,family ="binomial",data=titanic3)
summary(glm2)
```






# Cross Validation


```{r}
set.seed(243)
n<-nrow(titanic3)
train_index<-sample(1:n,round(0.7*n))
titanic_train<-titanic3[train_index, ]
titanic_test<-titanic3[-train_index, ]
```



Regression Summary on test model
```{r}
glm1<-glm(Survived~Age+Sex+Pclass,family ="binomial",data=titanic_test)
summary(glm1)
```

Regression Summary on Train
```{r}
glm3<-glm(Survived~Age+Pclass+Sex,family="binomial",data=titanic_train)
summary(glm3)
```







# Confusion Matrix 
Accuracy Specificity Sensitivity


```{r}
prob<-predict(glm1,newdata = titanic_test,type="response")
preds<-ifelse(prob>0.5,"yes","no")
```






```{r}
cm<-table(predicted=preds,actual=titanic_test$Survived)
addmargins(cm)
```

# Accuracy Percent correctly classified
```{r}
(100+78)/214
```
# Sensitivity Percent of people survived correctly classified (1)

```{r}
(78/98)
```
# Specificity Percent of people did not survived correctly classified (0)
```{r}
(100/116)
```
# Roc curve

 
```{r}

library(pROC)

roc_obj<-roc(titanic_test$Survived,prob)
plot(1-roc_obj$specificities,roc_obj$sensitivities,type="l",
 xlab="1-Specificity",ylab="Sensitivity")

points(x=100/116,y=78/98,col="red",pch=19)
abline(0,1,lty=2)


```
 
 
```{r}
auc(roc_obj)
```
 
 
# Predict 

```{r}
new_x<-data.frame(Age=25,Pclass='3',Sex='male')
predict(glm1,newdata = new_x,type="response")
```


